### 2024-06-16 doc/Thesis/chapter/01-introduction.tex
TD: intro

%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Photovoltaics (PV) is one viable option for becoming carbon neutral. 
Furthermore, 
it uses the sun's energy directly in contrast to other energy sources (e.g. wind, water or even carbon based) and therefore 
it is fit to be used in energy harvesting projects like futuristic Dyson spheres\cite{dyson1960search} which harness the whole power output of the sun.
%
One sort of PV are CIGS (copper indium gallium sulfide) cells\cite{Vasekar2010}. 
Due to their large absorption coefficient (compared to silicon based cells), less material is needed and they can be made thinner and flexible. 
%\td{was sind vorteile?}
In order to make a module, multiple cells are operated in series. 
The cells must be applied to a non-conducting surface.
Glass is a popular non-conducting substrate, but very rigid and brittle. 
An alternative is steel, which is ductile, inexpensive and highly available, but conducting. 
An insulating layer must therefore be applied to the steel substrate before any CIGS cells can be synthesised on top.
Polymers would be a obvious choice if not for its low thermal stability which makes high production temperatures impractical.
A non-toxic material which is suitable for the insulation is \ch{ZrO2}. 
%An economic and scalable method is doctor blading via a sol-gel process. 
Sol-gel roll-to-roll coating processes (e.g. tape casting) are economic and scalable methods to apply liquid precursors to substrates.
Sol-gel processes often produce porous layers, though. 
In this work a dense, insulating and homogeneous layer is pursued. 
Machine learning can help to uncover complex non-linear relations, such as the 
dependence of the thickness and resistance of the resulting layer on production factors.
%\td{influence} of the production factors on the thickness and resistance of the resulting layer.
The minimization of the conductance of the layer is performed with a particle swarm optimization 
algorithm which has the coating process variables as input. 
%The resulting optimum is compared with other optimization methods.
%\td{and how do you transfer knowledge ...}

@@

The remainder of this work is organized with chapter 
\ref{sec:theoretical} giving 
%some background information on topics of PV, \td{material science} and \td{computational science (more detail)} which were used in this work. 
information on the general working principles of PV, the structure, characteristics and properties of materials which were used and computational, statistical and machine learning methods for data processing.

>>>>

%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Photovoltaics (PV) is a viable renewable energy source towards energy neutrality.
Furthermore, 
it uses the sun's energy directly in contrast to other energy sources (e.g. wind, water or even carbon based) and therefore 
it is fit to be used in energy harvesting projects like futuristic Dyson spheres\cite{dyson1960search, kardashev1964transmission} which harness the whole power output of the sun.
%
One type  of thin film PV is based on the CIGS (copper indium gallium sulfide) semiconductor absorber\cite{Vasekar2010}. 
Due to the large light absorption coefficient of CIGS (compared to silicon), less absorber material is needed (a couple of micrometers) and the PV cell can be made thinner and flexible. 
%\td{was sind vorteile?}
In order to make a module, multiple solar cells are connected in series. 
The solar cells must be deposited on a non-conducting surface.
Glass is a popular non-conducting substrate, but rigid and brittle. 
A flexible alternative is steel foil, which is ductile, inexpensive and highly available, but electrically conducting. 
An insulating layer must therefore be applied to the steel substrate before any CIGS cells can be deposited on top.
Polymers would be a choice if not for their low thermal stability which does not permit high production temperatures.
A non-toxic material which is suitable for the insulation is zirconium oxide (\ch{ZrO2}). 
%An economic and scalable method is doctor blading via a sol-gel process. 
Sol-gel roll-to-roll coating processes (e.g. tape casting) are economic and scalable methods to apply liquid precursors to substrates, and have been also reported for the deposition of \ch{ZrO2}\cite{yeo1998design,michalek2015comparison}.
Sol-gel processes often produce porous layers, though.

In this work a dense, insulating and homogeneous layer of \ch{ZrO2} is pursued. 
Machine learning can help to uncover complex non-linear relations, such as the 
dependence of the thickness and resistance of the deposited layer on the coating parameters.
%\td{influence} of the production factors on the thickness and resistance of the resulting layer.
The minimization of the electrical conductance of the layer is performed with a particle swarm optimization 
algorithm which has the coating process variables as input. 
%The resulting optimum is compared with other optimization methods.
%\td{and how do you transfer knowledge ...}

@@

This work is organized as follows: chapter 
\ref{sec:theoretical} gives 
%some background information on topics of PV, \td{material science} and \td{computational science (more detail)} which were used in this work. 
information on the general working principles of PV, the structure, characteristics and properties of materials which were used and the employed computational, statistical and machine learning methods for data processing.

### 2024-06-16 doc/Thesis/chapter/03-experimental.tex
TD: intro

%The \td{\gls{1f}} was closest to the recipe proposed by Hu~et~al.~\cite{Hu2016}. 
The other four buthanolic solutions (\gls{2f}, \gls{3f}, \gls{4f} and \gls{5f}) were similar 
but with higher concentrations of \gls{zrpro} (see table \ref{tab:rec2})
with the aim of producing thicker layers.
%\td{p34}
Solvents (butane-1,2-diol, \gls{buoh} and Propan-1-ol) and chelating agents 
(\gls{acac} and citric acid) were tested and later in the process - just before 
starting the optimization of the process variables
%the \td{particle swarm optimisation} started 
- the stabilization compound (\gls{acoh}) was changed to \gls{ipo}.
The most promising combination of solvent, chelating agent and stabilization reagent was 
\gls{buoh}, \gls{acac} and \gls{ipo}, respectively, which was used for the final optimization.
\ds{
The main differences between the used recipe and the recipe mentioned in \cite{Hu2016} were 
\td{precursor (transition metal complex \gls{zrpro}	\gls{vs} post-transition metal complex aluminium isopropoxide \ch{Al(PrO)3}), solvent (\gls{buoh} \gls{vs} 2-ethoxyethanol \ch{EtOEtOH}), reaction temperature 
(room temperature \gls{vs} \SI{105}{\celsius}), stirring time (15/15/\SI{30}{\minute}
\gls{vs} 30/30/\SI{120}{\minute}), application process (doctor blading \gls{vs} spin coating), 
the heat treatment between layers (\SI{200}{\celsius} \gls{vs} \SI{200}{\celsius} and then \SI{400}
{\celsius}) and the calcination temperature (\SI{400}{\celsius} \gls{vs}
\SI{500}{\celsius}).
( so everything is different!! now I'm confused? you dream up a recipe and optimize that? not how I would do that! also: quite a difference between alpro3 and zrpro4)}
}
%me          hu
%Zr(OPr)4    Al(iPrO)3   
%1-BuOH      2-MeO-EtOH  
%RT          80-105
%15-15-30    30-30-120
%C          spin coating
%200C        200/400C
%400C        500C
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% PREOPTIMISATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Pre-optimization of Coating Procedure}
\label{sec:exp-preopt}
%\td{preopt of what? recipe?}
%\td{the choice of grenzen for \gls{doe} was done by biotic reinforcement learning (i.e. my brain)}
%\td{Screening}
%244 - 93 aquatic - 103 testing - 191 buthanol - 206 preopt - 244 emma
% 93 aq - 20 adapting Hu2016 - 88 testing process vars - 15 pre-opt - 38 emma (3 failed samples)
244 samples were produced: 93 samples with the aquatic recipes (see section \ref{sec:exp-sol-aq}), 20 samples for adapting the recipe from \cite{Hu2016}, 88 samples for testing coating process variables, 15 samples in pre-optimisation to find fitting constraints for the final optimization (see section \ref{sec:ss}).

>>>>

%The \td{\gls{1f}} was closest to the recipe proposed by Hu~et~al.~\cite{Hu2016}. 
The other four buthanolic solutions (\gls{2f}, \gls{3f}, \gls{4f} and \gls{5f}) were similar 
but with higher concentrations of \gls{zrpro} (see table \ref{tab:rec2})
with the aim of producing thicker layers.
%\td{p34}
Solvents (butane-1,2-diol, \gls{buoh} and Propan-1-ol) and chelating agents 
(\gls{acac} and citric acid) were tested and later in the process - just before 
starting the optimization of the process variables
%the \td{particle swarm optimization} started 
- the stabilization compound (\gls{acoh}) was changed to \gls{ipo}.
The most promising combination of solvent, chelating agent and stabilization reagent was 
\gls{buoh}, \gls{acac} and \gls{ipo}, respectively, which was used for the final optimization.
\ds{
The main differences between the used recipe and the recipe mentioned in \cite{Hu2016} were 
\td{precursor (transition metal complex \gls{zrpro}	\gls{vs} post-transition metal complex aluminium isopropoxide \ch{Al(PrO)3}), solvent (\gls{buoh} \gls{vs} 2-ethoxyethanol \ch{EtOEtOH}), reaction temperature 
(room temperature \gls{vs} \SI{105}{\celsius}), stirring time (15/15/\SI{30}{\minute}
\gls{vs} 30/30/\SI{120}{\minute}), application process (doctor blading \gls{vs} spin coating), 
the heat treatment between layers (\SI{200}{\celsius} \gls{vs} \SI{200}{\celsius} and then \SI{400}
{\celsius}) and the calcination temperature (\SI{400}{\celsius} \gls{vs}
\SI{500}{\celsius}).
( so everything is different!! now I'm confused? you dream up a recipe and optimize that? not how I would do that! also: quite a difference between alpro3 and zrpro4)}
}
%me          hu
%Zr(OPr)4    Al(iPrO)3   
%1-BuOH      2-MeO-EtOH  
%RT          80-105
%15-15-30    30-30-120
%C          spin coating
%200C        200/400C
%400C        500C
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% PREOPTIMIZATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Pre-optimization of Coating Procedure}
\label{sec:exp-preopt}
%\td{preopt of what? recipe?}
%\td{the choice of grenzen for \gls{doe} was done by biotic reinforcement learning (i.e. my brain)}
%\td{Screening}
%244 - 93 aquatic - 103 testing - 191 buthanol - 206 preopt - 244 emma
% 93 aq - 20 adapting Hu2016 - 88 testing process vars - 15 pre-opt - 38 emma (3 failed samples)
244 samples were produced: 93 samples with the aquatic recipes (see section \ref{sec:exp-sol-aq}), 20 samples for adapting the recipe from \cite{Hu2016}, 88 samples for testing coating process variables, 15 samples in pre-optimization to find fitting constraints for the final optimization (see section \ref{sec:ss}).

### 2024-06-16 doc/Thesis/chapter/052-post-emma.tex
feinschliff
TD: intro

\section{Post-EMMA}
\label{sec:res-post-emma}
%describe what awaits the reader in this chapter:
In this section the experimental results are analyzed with different methods and compared 
with the optimization method EMMA which was integrated into the experiment selection process. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsection{ANOVA}\label{sec:res-anova}
%\textbf{EMMA}
The \gls{rf}s produced by the last iteration of \gls{emma} (see equations \ref{eq:emma-phd4} and \ref{eq:emma-G4}) put a high significance
%/effect/correlation
on the calcination temperature $T_{cal}$ with regard to the 
measures of the conductance. 
\Gls{anova} is used to double check this. 
%Now \gls{anova} can be used to check if the data 
%\td{ANOVA was used to check if \gls{bf} identified by \gls{emma} are reasonable.}

@@

%\todo{what was fitted how?}
The data obtained from the \gls{emma} optimisation was used to fit a linear model. 
The biggest difference between the linear model and \gls{emma} is that the linear regression function will include all input variables, that the \gls{bf}s are strictly linear and that there are no interaction terms. 
The coefficients of the $n_L$ term have the same sign in equations \ref{eq:emma-phd3}, \ref{eq:emma-G3}, \ref{eq:emma-phd4}, \ref{eq:emma-G4} (\gls{emma} \gls{rf}s) and \ref{eq:linreg-phd}, \ref{eq:linreg-G} and have comparable magnitudes too. 
%
%Initially, it was thought that the resulting layer and thus resistance of a sample is mainly influenced by
%but their coefficients are the smallest in absolute values. 
%
\begin{align}
	\begin{split}
		\label{eq:linreg-phd}
		\hat{\rho} =&  -0.022\cdot c_{zr} -0.022\cdot n_L -0.0029\cdot v_{C} + 0.0058\cdot T_{C} \\
		& -8.5\cdot 10^{-5}\cdot v_{cal} + 0.0026\cdot T_{cal} -0.76
	\end{split}
	\\
	\begin{split}
		\label{eq:linreg-G}
		\hat{\gamma} =&  \,\,\qquad 3.2\cdot c_{zr} \,\, - 0.97\cdot n_L \,\,\quad - 1.2\cdot v_{C}  \,\,\,\quad +0.2\cdot T_{C} \\
			& \qquad - 0.014\cdot v_{cal} \quad + 0.13\cdot T_{cal} + 7.2
%		\hat{\gamma} ={} & 3.2\cdot c_{zr} - 0.97\cdot n_L - 1.2\cdot v_{C} + 0.2\cdot T_{C} \\
%			& - 0.014\cdot v_{cal} + 0.13\cdot T_{cal} + 7.2
	\end{split}
\end{align}
%
All terms in equations \ref{eq:linreg-phd} and \ref{eq:linreg-G} have the same sign 
except $c_{zr}$ and the intercept. 
%
More particularly, $T_{cal}$ and $T_{C}$ have positive coefficients, i.e. a negative influence on the resistance 
and $n_L$, $v_{C}$ and $v_{cal}$ have negative coefficients, i.e. a positive influence on resistance. 
An indication that the data is strongly tainted by noise (see also section \ref{sec:res-anova}) is the low $R^2$ score of 0.41 of $\hat\rho$, 
which is (sad but true) even undercut by the $R^2$ of linear fit of $\hat\gamma$, 0.34. 
%The coefficients, though share the signs. 
%This is only true if the extended data set is used and therefore again rather by chance. 
When the linear regression is trained on the whole data set, all terms have the same sign compared to the \gls{emma} data set trained linear model. 
%It is even more astounding that \gls{emma} managed to decrease the average of $\gamma$ an $\rho$ with each generation (see figure \ref{fig:emma-gen}.
$v_{cal}$ and $n_L$ are perfectly predicted by linear regression as there is an exact direct proportionality and thus are not displayed here. 
%
\begin{table}[htb]
	\center
	\begin{tabular}{cccccccc}
		        & $c_{zr}$      & $n_L$     & $v_{C}$      & $T_{C}$      & $v_{cal}$     & $T_{cal}$\\
				\hline\hline
				$\hat\rho$          &2.04   &46.58  &1.15   &9.21   &13.50  &27.52\\
				$\hat\gamma$        &10.24  &7.10   &16.46  &10.97  &7.68   &47.55\\
				\hline\hline
	\end{tabular}
	\label{tab:lin-reg-influence}
	\caption{Influences of input variables on output variables in percent according to linear regression.}
\end{table}

@@

%\iffalse
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% ML %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% GRID SEARACH %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsection{Grid Search, KRR and SVM}
The optimal parameters for each combination of 
\textit{optimizand} ($\gamma$ and $\rho$) and method (KRR and SVM) 
can be seen in table \ref{tab:grid-search}. 
The parameters are often extrema.
The hyperparameter $\gamma_{ml}$ took the smallest possible value (within the grid search) twice. 
In the polynomial kernel this leads to a lower influence of the input variables with respect to the intercept. 
The range of the hyperparameter $\alpha$ (see section~\ref{sec:ml-methods}) was 0.01--10 in the grid search. 
So, 2 and 10 are high values for the regularization parameter $\alpha$ of \gls{krr}.
The hyperparameter $\varepsilon$ specifies the size of the tube within which data does not contribute to the loss 
and the value 1 is the maximum for $\varepsilon$ during this grid search. 
%\td{why can R2 be negative? https://stats.stackexchange.com/a/279358/374563 } 
%The value 1 for $\varepsilon$ is the highest possible, 
%$C$ is regularization parameter for SVM and $\varepsilon$ is var which defines loss less region in soft margin SVM}
All these extreme values of hyperparameters stimulate regularization and indicate noisy and difficult to fit data.
\begin{table}
    \center
    \begin{tabular}{cccccccc}
        \hline\hline
        method  &$R^2$   &kernel &degree &$\gamma_{ml}$   &$\alpha$    &$C$    &$\varepsilon$\\
        \hline
        KRR($\gamma$) & $-0.50 \pm 0.25$  &poly   &1  &0.01   &2 &-&-\\
        KRR($\rho  $) & $-0.45 \pm 0.52$  &rbf    &-   &0.2   &10&-&-\\
        SVM($\gamma$) & $-0.37 \pm 0.39$  &poly   &2  &0.5    &-&0.7  &1.0  \\
        SVM($\rho  $) & $-0.95 \pm 0.44$  &poly   &3  &0.01   &-&0.1  &0.1  \\
        \hline\hline
    \end{tabular}
    \caption{$R^2$ values and best hyperparameters for each \textit{optimizand}-method-combination}
    \label{tab:grid-search}
\end{table}
% R2
The $R^2$ values were calculated for each of the models using cross validation. 
Resulting $R^2$ are all below zero (see table~\ref{tab:grid-search}). 
A negative $R^2$ value means that the prediction provided by the model is worse than predicting only the mean of $\gamma$ and $\rho$ (see \ref{eq:r2}). 
%\td{how can R2 be below zero?}
% https://scikit-learn.org/stable/modules/generated/sklearn.kernel_ridge.KernelRidge.html#sklearn.kernel_ridge.KernelRidge.score

>>>>

\section{Post-EMMA}
\label{sec:res-post-emma}
%describe what awaits the reader in this chapter:
In this section the experimental results are analyzed with different methods and compared 
with the optimization method EMMA which was integrated into the experiment selection process. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsection{Analysis of Variance}
\label{sec:res-anova}
%\textbf{EMMA}
The \gls{rf}s produced by the last iteration of \gls{emma} (see equations \ref{eq:emma-phd4} and \ref{eq:emma-G4}) put a high significance
%/effect/correlation
on the calcination temperature $T_{cal}$ with regard to the 
measures of the conductance. 
\Gls{anova} is used to double check this. 
%Now \gls{anova} can be used to check if the data 
%\td{ANOVA was used to check if \gls{bf} identified by \gls{emma} are reasonable.}

@@

%\todo{what was fitted how?}
The data obtained from the \gls{emma} optimization was used to fit a linear model. 
The biggest difference between the linear model and \gls{emma} is that the linear regression function will include all input variables, that the \gls{bf}s are strictly linear and that there are no interaction terms. 
The coefficients of the $n_L$ term have the same sign in equations \ref{eq:emma-phd3}, \ref{eq:emma-G3}, \ref{eq:emma-phd4}, \ref{eq:emma-G4} (\gls{emma} \gls{rf}s) and \ref{eq:linreg-phd}, \ref{eq:linreg-G} and have comparable magnitudes too. 
%
%Initially, it was thought that the resulting layer and thus resistance of a sample is mainly influenced by
%but their coefficients are the smallest in absolute values. 
%
\begin{align}
	\begin{split}
		\label{eq:linreg-phd}
		\hat{\rho} =&  -0.022\cdot c_{zr} -0.022\cdot n_L -0.0029\cdot v_{C} + 0.0058\cdot T_{C} \\
		& -8.5\cdot 10^{-5}\cdot v_{cal} + 0.0026\cdot T_{cal} -0.76
	\end{split}
	\\
	\begin{split}
		\label{eq:linreg-G}
		\hat{\gamma} =&  \,\,\qquad 3.2\cdot c_{zr} \,\, - 0.97\cdot n_L \,\,\quad - 1.2\cdot v_{C}  \,\,\,\quad +0.2\cdot T_{C} \\
			& \qquad - 0.014\cdot v_{cal} \quad + 0.13\cdot T_{cal} + 7.2
%		\hat{\gamma} ={} & 3.2\cdot c_{zr} - 0.97\cdot n_L - 1.2\cdot v_{C} + 0.2\cdot T_{C} \\
%			& - 0.014\cdot v_{cal} + 0.13\cdot T_{cal} + 7.2
	\end{split}
\end{align}
%
All terms in equations \ref{eq:linreg-phd} and \ref{eq:linreg-G} have the same sign 
except $c_{zr}$ and the intercept. 
%
More particularly, $T_{cal}$ and $T_{C}$ have positive coefficients, i.e. a negative influence on the resistance 
and $n_L$, $v_{C}$ and $v_{cal}$ have negative coefficients, i.e. a positive influence on resistance. 
An indication that the data is strongly tainted by noise (see also section \ref{sec:res-anova}) is the low $R^2$ score of 0.41 of $\hat\rho$, 
which is (sad but true) even undercut by the $R^2$ of linear fit of $\hat\gamma$, 0.34. 
%The coefficients, though share the signs. 
%This is only true if the extended data set is used and therefore again rather by chance. 
When the linear regression is trained on the whole data set, all terms have the same sign compared to the \gls{emma} data set trained linear model. 
%It is even more astounding that \gls{emma} managed to decrease the average of $\gamma$ an $\rho$ with each generation (see figure \ref{fig:emma-gen}.
$v_{cal}$ and $n_L$ are perfectly predicted by linear regression as there is an exact direct proportionality and thus are not displayed here. 
%
\begin{table}[htb]
	\center
	\begin{tabular}{cccccccc}
		        & $c_{zr}$      & $n_L$     & $v_{C}$      & $T_{C}$      & $v_{cal}$     & $T_{cal}$\\
				\hline\hline
				$\hat\rho$          &2.04   &46.58  &1.15   &9.21   &13.50  &27.52\\
				$\hat\gamma$        &10.24  &7.10   &16.46  &10.97  &7.68   &47.55\\
				\hline\hline
	\end{tabular}
	\label{tab:lin-reg-influence}
	\caption{Influences of input variables on output variables in percent according to linear regression.}
\end{table}

@@

%\iffalse
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% ML %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% GRID SEARACH %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%\clearpage
%\subsection{Grid Search, KRR and SVM}
\subsection{Grid Search, Kernel Ridge Regression and Support Vector Machine}

The optimal parameters for each combination of 
\textit{optimizand} ($\gamma$ and $\rho$) and method (KRR and SVM) 
can be seen in table \ref{tab:grid-search}. 
The parameters are often extrema.
The hyperparameter $\gamma_{ml}$ took the smallest possible value (within the grid search) twice. 
In the polynomial kernel this leads to a lower influence of the input variables with respect to the intercept. 
The range of the hyperparameter $\alpha$ (see section~\ref{sec:ml-methods}) was 0.01--10 in the grid search. 
So, 2 and 10 are high values for the regularization parameter $\alpha$ of \gls{krr}.
The hyperparameter $\varepsilon$ specifies the size of the tube within which data does not contribute to the loss 
and the value 1 is the maximum for $\varepsilon$ during this grid search. 
%\td{why can R2 be negative? https://stats.stackexchange.com/a/279358/374563 } 
%The value 1 for $\varepsilon$ is the highest possible, 
%$C$ is regularization parameter for SVM and $\varepsilon$ is var which defines loss less region in soft margin SVM}
All these extreme values of hyperparameters stimulate regularization and indicate noisy and difficult to fit data.
\begin{table}
    \center
    \begin{tabular}{cccccccc}
        \hline\hline
        method  &$R^2$   &kernel &degree &$\gamma_{ml}$   &$\alpha$    &$C$    &$\varepsilon$\\
        \hline
        KRR($\gamma$) & $-0.50 \pm 0.25$  &poly   &1  &0.01   &2 &-&-\\
        KRR($\rho  $) & $-0.45 \pm 0.52$  &rbf    &-   &0.2   &10&-&-\\
        SVM($\gamma$) & $-0.37 \pm 0.39$  &poly   &2  &0.5    &-&0.7  &1.0  \\
        SVM($\rho  $) & $-0.95 \pm 0.44$  &poly   &3  &0.01   &-&0.1  &0.1  \\
        \hline\hline
    \end{tabular}
    \caption{$R^2$ values and best hyperparameters for each \textit{optimizand}-method-combination}
    \label{tab:grid-search}
\end{table}
% R2
The $R^2$ values were calculated for each of the models using cross validation. 
Resulting $R^2$ are all below zero (see table~\ref{tab:grid-search}). 
A negative $R^2$ value means that the prediction provided by the model is worse than predicting only the mean of $\gamma$ and $\rho$ (see \ref{eq:r2}). 
%\td{how can R2 be below zero?}
% https://scikit-learn.org/stable/modules/generated/sklearn.kernel_ridge.KernelRidge.html#sklearn.kernel_ridge.KernelRidge.score
